### 2020-03-07 draft_ABP.tex
merge from overleaf

\usepackage{comment}
\input epsf.sty
\topmargin -.1cm
\textheight 21cm
\oddsidemargin 0.15cm 
\textwidth 14cm
\usepackage{cite}
\usepackage{epsfig,amssymb,euscript,xspace,xcolor}
\usepackage{amsmath,mathtools,empheq,amsthm,hyperref,graphicx}
\usepackage{mathrsfs,float}  
\usepackage{pgf,tikz,pgfplots}
\usetikzlibrary{arrows}
\usepackage[T1]{fontenc} 
\usepackage{tikz,caption,subcaption,marvosym} 
\usetikzlibrary{decorations.markings,arrows,snakes}
\usepackage[belowskip=-15pt,aboveskip=0pt]{caption}
\usepackage[skip=10pt]{caption} % example skip set to 2pt
\usepackage{comment}

@@

Generally, the big polyhdron of a stringy integral is not necessary to be a simplex.
It's known that stringy integrals associated to the $A_n$, $B_n$, $C_n$, $D_n$,
$E_6$, $E_7$, $E_8$, $F_2$ and $G_4$ type clusters are in this type. What's more,
they satisfy the so called $u$-equations with the form
\begin{equation}\label{perfectu}
	1-u_i=\prod_{j}u_j^{(i||j)},
\end{equation}
where $(i||j)\geq 0$ is a integral defined in the cluster algebra context \cite{}.
Varieties defined by $u$-equations associated with finite type clusters 
are called cluster configuration spaces. 
For this type equations, once $u_i$ goes to $0$, it forces some $u_j$ to go to $1$.
Therefore, these $u$-equations reveal the binary structure of the cluster
configuration spaces. ...

@@

\section*{Generalized permutahedra}

@@

 If $z_I =z_J$ whenever $|I| =|J|$, then  $ P_n^z(\{ z_I \})$ is the usual permutahedron. 
 \begin{itemize}
 \item The combinatorial structure of the generalised permutahedron depends only on the set $B$ of nonemepty subsets $I \subset [0,n]$ such that $y_I \geq 0$ which is called the {\it building set}. To describe the combinatorial structure we need the notion of {\it Nested complex} which we shall define now.
\section*{Nested Complex}
If $B$ additionally satisfies the following:

@@

\item {\bf Minkowski decomposition:} Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. For any $I \subset [0,n] $ let $\Delta_I ={\rm ConvexHull(e_i~|~i\in I)}$ denote the face of the $\Delta_{[0,n]}$. The polytope $P_n^y(\{y_I \})$ obtained as the Minkowski sum of simplices $\Delta_I$ scaled by  parameters $y_I \geq 0$ for all nonempty subsets $I \subset [0,n]$
 \bea
 P_n^y(\{y_I \})= \sum_{I \subset[0,n]} y_I . \Delta_I  \nonumber
 \eea
is the generalised permutahedron $P_n^z(\{z_I \})$ if $z_I = \sum_{J \subset I} y_J  ~{\rm for~all~nonempty} I \subset [0,n]$.
\footnote{Not all generalised permutahedra cannot be written as Minkowski sum of coordinate simplices. We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation.}

>>>>

\usepackage{comment}
\input epsf.sty
\topmargin -.1cm
\textheight 21cm
\oddsidemargin 0.15cm 
\textwidth 14cm
\usepackage{cite}
\usepackage{epsfig,amssymb,euscript,xspace,xcolor}
\usepackage{amsmath,mathtools,empheq,amsthm,hyperref,graphicx,paralist}
\usepackage{mathrsfs,float}  
\usepackage{pgf,tikz,pgfplots}
\usetikzlibrary{arrows}
\usepackage[T1]{fontenc} 
\usepackage{tikz,caption,subcaption,marvosym} 
\usetikzlibrary{decorations.markings,arrows,snakes}
\usepackage[belowskip=-15pt,aboveskip=0pt]{caption}
\usepackage[skip=10pt]{caption} % example skip set to 2pt
\usepackage{comment}

@@

Generally, the big polyhdron of a stringy integral is not necessary to be a simplex.
It's known that stringy integrals associated to the $A_n$, $B_n$, $C_n$, $D_n$,
$E_6$, $E_7$, $E_8$, $F_2$ and $G_4$ type clusters are in this type. What's more,
they satisfy the so called $u$-equations with the form
\begin{equation}\label{perfectu}
	1-u_i=\prod_{j}u_j^{(i||j)},
\end{equation}
where $(i||j)\geq 0$ is a integral defined in the cluster algebra context \cite{}.
Varieties defined by $u$-equations associated with finite type clusters 
are called cluster configuration spaces. 
For this type equations, once $u_i$ goes to $0$, it forces some $u_j$ to go to $1$.
Therefore, these $u$-equations reveal the binary structure of the cluster
configuration spaces.

@@

\subsection*{Generalized permutahedra}

@@

 If $z_I =z_J$ whenever $|I| =|J|$, then  $ P_n^z(\{ z_I \})$ is the usual permutahedron. 
 \begin{itemize}
 \item The combinatorial structure of the generalised permutahedron depends only on the set $B$ of nonemepty subsets $I \subset [0,n]$ such that $y_I \geq 0$ which is called the {\it building set}. To describe the combinatorial structure we need the notion of {\it Nested complex} which we shall define now.
 \end{itemize}

\subsection*{Nested Complex}
If $B$ additionally satisfies the following:
\begin{compactenum}[\quad (1)]
    \item If $I,J \in B$ and $I \cap J \neq \phi $, then $I \cup J \in B$.
    \item $B$ contains all singletons $\{ i\}$ for $i \in S$.
\end{compactenum}

A subset $N$ in the building set $B$ is called a {\it nested set} if it satisfies the following conditions:
\begin{compactenum}[\quad (1)]
    \item For any $I,J \in N$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.
    \item For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\cdots, J_k \in N$ their union $J_1 \cup \cdots \cup J_k$ is not in B.
    \item $N$ contains all maximal elements of $B$.
\end{compactenum}

@@

 \begin{itemize}
\item {\bf Minkowski decomposition:} Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. For any $I \subset [0,n] $ let $\Delta_I ={\rm ConvexHull(e_i~|~i\in I)}$ denote the face of the $\Delta_{[0,n]}$. The polytope $P_n^y(\{y_I \})$ obtained as the Minkowski sum of simplices $\Delta_I$ scaled by  parameters $y_I \geq 0$ for all nonempty subsets $I \subset [0,n]$
 \bea
 P_n^y(\{y_I \})= \sum_{I \subset[0,n]} y_I . \Delta_I  \nonumber
 \eea
is the generalised permutahedron $P_n^z(\{z_I \})$ if $z_I = \sum_{J \subset I} y_J  ~{\rm for~all~nonempty} I \subset [0,n]$.
\footnote{Not all generalised permutahedra cannot be written as Minkowski sum of coordinate simplices. We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation.}
